---
title: "AKI and Outcomes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## This loads in data, merges data
```{r Load Data}
AKI_rec <- read.delim("C:/Python27/git/AKI/output/AKI_2017-03-30-17-17-07-386000.txt", header=TRUE, quote="'", na.strings=c("{}", "None"))
admit_year <-read.delim("C:/Python27/git/OtherData/mimiciii_admission_year.csv", header=TRUE, sep=",")
AKI_rec <- merge(x=AKI_rec, y=admit_year,by.x="hadm_id", by.y="HADM_ID", all.x=TRUE)
#names(AKI_rec) <- gsub(".x", "", names(AKI_rec) )
```


## Cleans data
#### AKI - only patients with no AKI or stage 1-3 AKI are included.
#### ESRD - only patients without ESRD are included
#### hospital_expire_flag - Only patients who did not die in the hospital are included
#### AKI_discharge:
####-1 = there was admit creatinine missing, or there was AKI and discharge creatinine is missing.
####-1 = discharge creatinine is less than admit creatinine, but there was no AKI per KDIGO definition
####0 = there was no AKI
####1 = there was AKI then recovery
####2 = there was AKI and no recovery
####There is a thrid group that was never diagnosed with AKI, but leaves the hospital with a creatinine greater than the admit creatinine..
####Not sure what we should do about those. Nothing currently, they are under 0 (no AKI)
####If discharge creatinine was not documented and there was no AKI (per KDIGO), it will be 0
```{r Cleans data, gets subsets}
df_rec <- AKI_rec
df_rec <- df_rec[df_rec$AKI %in% c(0, 1, 2, 3) ,]
df_rec <- df_rec[df_rec$esrd %in% c(0) ,]
df_rec <- df_rec[df_rec$hospital_expire_flag %in% c(0) ,]
df_rec <- df_rec[df_rec$AKI_discharge %in% c(0,1,2) ,]
df_rec$age <-  ifelse(df_rec$age >150, 91.4, df_rec$age) 
df_rec <- df_rec[!(df_rec$YEAR %in% c(2012)),]
```


## Adds death columns
```{r adds death columns}
df_rec["Death_1_30"] <-  ifelse((df_rec$day_after_icu_discharge_death > 0) & (df_rec$day_after_icu_discharge_death<=30), 1, 0) 
df_rec["Death_31_90"] <-  ifelse((df_rec$day_after_icu_discharge_death > 30) & (df_rec$day_after_icu_discharge_death<=90), 1, 0) 
df_rec["Death_91_450"] <-  ifelse((df_rec$day_after_icu_discharge_death > 90) & (df_rec$day_after_icu_discharge_death<=450), 1, 0) 
#df_rec["No_death_by_450"] <- <-  ifelse((df_rec$day_after_icu_discharge_death>450) || df_rec$day_after_icu_discharge_death, 1, 0) 
#is.na(day_after_icu_discharge_death) - can add it in later for logistics
df_rec["AKI_bin"] <-  ifelse((df_rec$AKI > 0) , 1, 0) 
```
## Add new creatinine column
#### If the creatinine at discharge is greater than 3.
```{r}
df_rec["cr_gr_3"] <- ifelse((df_rec$discreat>3) , 1, 0)
```

## AKI BIN 
#### 

```{r add discharge bin}
#df_rec["AKI_discharge_bin"] <- ifelse(((df_rec$AKI_discharge == 0) | (df_rec$AKI_discharge == 1) ), 0, 1)
#df_rec["AKI_discharge_bin"] <- ifelse((df_rec$AKI_discharge == 0),0, ifelse(df_rec$AKI_discharge == 1), 1, NA)

#df_rec["AKI_discharge_bin"] <-  ifelse((df_rec$AKI_discharge == 0), 0, #(ifelse(df_rec$AKI_discharge == 2), 1, 2)) 
                                   
#                                   | (df_rec$AKI_discharge == 1) ), 0, 1)


df_rec["AKI_discharge_bin"] <-   
ifelse(df_rec$AKI_discharge == 0, 0,
ifelse(df_rec$AKI_discharge == 2, 1, NA))

```

## Add Death Buckets
####- If death is withink 30 days, then 1
####- within 30-90, then 2
####- within 90-450, then 3
```{r death buckets}
df_rec["Death_buckets"] <-   
ifelse(df_rec$day_after_icu_discharge_death > 90 & (df_rec$day_after_icu_discharge_death <= 450), 3,
ifelse(df_rec$day_after_icu_discharge_death > 30 & (df_rec$day_after_icu_discharge_death <= 90), 2,
ifelse(df_rec$day_after_icu_discharge_death >= 0 & (df_rec$day_after_icu_discharge_death <= 30), 1, 0)))

```


```{r get table variables, categorical variables}


listVars <- c(
            "gender",
            "los_hospital",
            "age",
            "hospital_expire_flag",
            "los_icu",
            "oasis",
            "admission_type",
            "first_service",
            "rrt",
            "AKI",
#            "Death_1_30",
#            "Death_31_90",
#            "Death_91_450",
            "Death_buckets",
            "AKI_discharge_bin",
            "cr_gr_3"
            )
catVars <- c("gender",
             "hospital_expire_flag",
             "rrt",
             "AKI",
             "admission_type",
             "first_service",
 #           "Death_1_30",
  #          "Death_31_90",
  #          "Death_91_450",
             "Death_buckets",
            "AKI_discharge_bin",
            "cr_gr_3"
             )
library(dplyr)
library(tableone)
```


```{r weibull distribution}
library(muhaz)

df_temp = df_rec
df_temp["status"] <- 
ifelse((df_temp$day_after_icu_discharge_death <= 0) , 1,
ifelse (df_temp$day_after_icu_discharge_death <= 450, 1, 0))

df_temp['status'] <-  ifelse(is.na(df_temp$day_after_icu_discharge_death), 0, df_temp$status)
#when I tried to do a if/else, the na's didn't catch under else

df_temp["mod_day_after_icu_discharge_death"] <- 
ifelse((df_temp$day_after_icu_discharge_death <= 0) , 1, 
ifelse(df_temp$day_after_icu_discharge_death >450, 450, 
ifelse(df_temp$day_after_icu_discharge_death <=450, df_temp$day_after_icu_discharge_death, 450)))

df_temp["mod_day_after_icu_discharge_death"] <-
  ifelse(is.na(df_temp$day_after_icu_discharge_death), 450, df_temp$mod_day_after_icu_discharge_death)


#fit1 <- survreg(Surv(mod_day_after_icu_discharge_death)~AKI_bin, data=df_temp, #dist="exponential")
#summary(fit1)
#fit1 <- survreg(Surv(mod_day_after_icu_discharge_death)~AKI_bin, data=df_temp, dist="weibull")
#summary(fit1)

#muhaz.fit = muhaz(df_temp$mod_day_after_icu_discharge_death ,  df_temp$status, max.time = 450)
#
#
#muhazrate = muhaz.fit$haz.est
#plot(muhaz.fit)
#plot(muhazrate)

#kpfit<- kphaz.fit(time = df_temp$mod_day_after_icu_discharge_death, status= df_temp$status, strata = df_temp$AKI_bin)
#kphaz.plot(kpfit[2])

AKI_bin0 = df_temp[df_temp$AKI_bin == 0,]
AKI_bin1 = df_temp[df_temp$AKI_bin == 1,]

muhaz0.fit = muhaz(AKI_bin0$mod_day_after_icu_discharge_death ,  AKI_bin0$status, max.time = 450)
muhazrate0 = muhaz0.fit$haz.est
#plot(muhaz.fit)
#plot(muhazrate)

muhaz1.fit = muhaz(AKI_bin1$mod_day_after_icu_discharge_death ,  AKI_bin1$status, max.time = 450)
muhazrate1 = muhaz1.fit$haz.est

plot(muhaz0.fit, col="red")
lines(muhaz1.fit, col="blue")
#plot(muhazrate)
```
